Jane, John … Leslie? A Historical Method for Algorithmic Gender Detection

### 2014-09-19 article.Rmd
Trying to comply with some bizarre citation style

Bird et al. 2009. Bird, Steve, Edward Loper, and Ewan Klein, *Natural Language Processing with Python* (O’Reilly, 2009).

Brubaker and Cooper 2000. Brubaker, Rogers, and Frederick Cooper. “Beyond ‘identity.’” *Theory and Society* 29.1 (2000): 1–47.

Butler 1989. Butler, Judith. *Gender Trouble: Feminism and the Subversion of Identity*. New York: Routledge, 1990.

Butler 1993. Butler, Judith. *Bodies That Matter: On the Discursive Limits of Sex*. New York: Routledge, 1993.

Canaday 2011. Canaday, Margot. *The Straight State: Sexuality and Citizenship in Twentieth-Century America*. Princeton, N.J.: Princeton University Press, 2011.

Genderize.io 2014-. *Genderize.io*. Accessed 15 September 2014, http://genderize.io/.

Goldstone and Underwood 2014. Goldstone, Andrew, and Ted Underwood. "The Quiet Transformations of Literary Studies: What Thirteen Thousand Scholars Could Tell Us." *New Literary History* (Forthcoming 2014).

Healy 2013. Healy, Kieran. "Using Metadata to Find Paul Revere." *kieranhealy.org*. 9 June 2013, http://kieranhealy.org/blog/archives/2013/06/09/using-metadata-to-find-paul-revere/

Landrum 2014. Landrum, Shane. "The State's Big Family Bible: Birth Certificates, Personal Identity, and Citizenship in the United States, 1840--1950." PhD dissertation, Brandeis University, August 2014.

Muenchen 2014-. Muenchen, Robert A. "The Popularity of Data Analysis Software," *r4stats.com*. Accessed 12 September 2014, http://r4stats.com/articles/popularity/.

Pascoe 2009. Pascoe, Peggy. *What Comes Naturally: Miscegenation Law and the Making of Race in America*. Oxford University Press, USA, 2009.

Piatetsky 2013. Piatetsky, Gregory. "Top Languages for analytics, data mining, data science," *KDN Nuggets*. 27 August 2013, http://www.kdnuggets.com/2013/08/languages-for-analytics-data-mining-data-science.html.

R Core Team 2014-. R Core Team, *R: A language and environment for statistical computing*. R Foundation for Statistical Computing, Vienna, Austria, 2014. <http://www.R-project.org/>

Ruggles et al. 2010. Ruggles, Steven, J. Trent Alexander, Katie Genadek, Ronald Goeken, Matthew B. Schroeder, and Matthew Sobek. Integrated Public Use Microdata Series: Version 5.0 [Machine-readable database]. Minneapolis, MN: Minnesota Population Center [producer and distributor], 2010.

Social Security Administration 2014-a. Social Security Administration, "Baby Names from Social Security Card Applications-National Level Data". Data.gov dataset ID US-GOV-SSA-338. Accessed 31 August 2014, http://catalog.data.gov/dataset/baby-names-from-social-security-card-applications-national-level-data

Social Security Administration 2014-b. Social Security Administration, "Baby Names from Social Security Card Applications-Data by State and District of Columbia." Data.gov dataset ID US-GOV-SSA-339. Accessed 31 August 2014, http://catalog.data.gov/dataset/baby-names-from-social-security-card-applications-data-by-state-and-district-of-

Weingart 2014. Weingart, Scott. "The Moral Role of DH in a Data-Driven World." *the scottbot irregular*. 9 September 2014, http://www.scottbot.net/HIAL/?p=40944

Wickham 2014. Hadley Wickham, "Tidy Data." *Journal of Statistical Software*, 50 (2014): http://www.jstatsoft.org/v59/i10.

Wickham and Francois 2014. Wickham, Hadley and Romain Francois, *dplyr: dplyr: a grammar of data manipulation*. R package version 0.2 (2014): <http://CRAN.R-project.org/package=dplyr>.

World Bank 2014-. World Bank. "Life expectancy at birth, total (years)." *World Bank Open Data*. Accessed 12 September 2014, http://data.worldbank.org/indicator/SP.DYN.LE00.IN.

>>>>

[Bird et al. 2009] Bird, Steve, Edward Loper, and Ewan Klein. *Natural Language Processing with Python* (O’Reilly, 2009).

[Brubaker and Cooper 2000] Brubaker, Rogers, and Frederick Cooper. "Beyond 'identity.'" *Theory and Society* 29.1 (2000): 1–47.

[Butler 1989] Butler, Judith. *Gender Trouble: Feminism and the Subversion of Identity*. New York: Routledge, 1990.

[Butler 1993] Butler, Judith. *Bodies That Matter: On the Discursive Limits of Sex*. New York: Routledge, 1993.

[Canaday 2011] Canaday, Margot. *The Straight State: Sexuality and Citizenship in Twentieth-Century America*. Princeton, N.J.: Princeton University Press, 2011.

[Genderize.io 2014-] *Genderize.io*. Accessed 15 September 2014, http://genderize.io/.

[Goldstone and Underwood 2014] Goldstone, Andrew, and Ted Underwood. "The Quiet Transformations of Literary Studies: What Thirteen Thousand Scholars Could Tell Us." *New Literary History* (Forthcoming 2014).

[Healy 2013] Healy, Kieran. "Using Metadata to Find Paul Revere." *kieranhealy.org*. 9 June 2013, http://kieranhealy.org/blog/archives/2013/06/09/using-metadata-to-find-paul-revere/

[Landrum 2014] Landrum, Shane. "The State's Big Family Bible: Birth Certificates, Personal Identity, and Citizenship in the United States, 1840--1950." PhD dissertation, Brandeis University, August 2014.

[Muenchen 2014-] Muenchen, Robert A. "The Popularity of Data Analysis Software," *r4stats.com*. Accessed 12 September 2014, http://r4stats.com/articles/popularity/.

[Pascoe 2009] Pascoe, Peggy. *What Comes Naturally: Miscegenation Law and the Making of Race in America*. Oxford University Press, USA, 2009.

[Piatetsky 2013] Piatetsky, Gregory. "Top Languages for analytics, data mining, data science," *KDN Nuggets*. 27 August 2013, http://www.kdnuggets.com/2013/08/languages-for-analytics-data-mining-data-science.html.

[R Core Team 2014-] R Core Team. *R: A language and environment for statistical computing*. R Foundation for Statistical Computing, Vienna, Austria, 2014. <http://www.R-project.org/>

[Ruggles et al. 2010] Ruggles, Steven, J. Trent Alexander, Katie Genadek, Ronald Goeken, Matthew B. Schroeder, and Matthew Sobek. Integrated Public Use Microdata Series: Version 5.0 [Machine-readable database]. Minneapolis, MN: Minnesota Population Center [producer and distributor], 2010.

[Social Security Administration 2014-a] Social Security Administration. "Baby Names from Social Security Card Applications-National Level Data". Data.gov dataset ID US-GOV-SSA-338. Accessed 31 August 2014, http://catalog.data.gov/dataset/baby-names-from-social-security-card-applications-national-level-data

[Social Security Administration 2014-b] Social Security Administration. "Baby Names from Social Security Card Applications-Data by State and District of Columbia." Data.gov dataset ID US-GOV-SSA-339. Accessed 31 August 2014, http://catalog.data.gov/dataset/baby-names-from-social-security-card-applications-data-by-state-and-district-of-

[Weingart 2014] Weingart, Scott. "The Moral Role of DH in a Data-Driven World." *the scottbot irregular*. 9 September 2014, http://www.scottbot.net/HIAL/?p=40944

[Wickham 2014] Wickham, Hadley. "Tidy Data." *Journal of Statistical Software*, 50 (2014): http://www.jstatsoft.org/v59/i10.

[Wickham and Francois 2014] Wickham, Hadley, and Romain Francois. *dplyr: dplyr: a grammar of data manipulation*. R package version 0.2 (2014): <http://CRAN.R-project.org/package=dplyr>.

[World Bank 2014-] World Bank. "Life expectancy at birth, total (years)." *World Bank Open Data*. Accessed 12 September 2014, http://data.worldbank.org/indicator/SP.DYN.LE00.IN.
